DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-26 paper/intro.tex
Update introduction

% DeepPicar introduction
In this paper, we present DeepPicar, a low-cost autonomous car
platform for research. From a hardware perspective,
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are affordable
components (less than \$100 in total).
The DeepPicar, however, employs state-of-the-art AI
technologies, including a vision-based end-to-end control system that
utilizes a deep convolutional neural network (CNN).
The network receives an image frame from a single forward
looking camera as input and generates a predicted steering angle
value as output at each control period in \emph{real-time}.
The network has 9 layers, about 27 million connections
and 250 thousand parameters (weights).
The network architecture is identical to that of NVIDIA's DAVE-2
self-driving car~\cite{Bojarski2016}, which uses a much more powerful
computer (Drive PX computer~\cite{drivepx}) than a Raspberry Pi~3.
We chose to use a Pi 3 not only because it is affordable, but also because it is representative
of today's mainstream low-end embedded multicore platforms found in
smartphones and other embedded devices.

@@

% how we trained (maybe moved to a later section)
We apply a standard imitation learning methodology to train the car to
follow tracks on the ground. We collect data for
training and validation by manually
controlling the RC car and recording the vision (from the webcam
mounted on the RC-car) and the human control inputs. We then train the
network offline using the collected data on a desktop computer, which
is equipped with a NVIDIA GTX 1060 GPU. Finally, the trained network is copied
back to the Raspberry Pi, which is then used to perform inference
operations---locally on the Pi---in the car's main control loop in
real-time. For real-time control, each inference operation must
be completed within the desired control period (e.g., 50 ms period for
20 Hz control frequency).
% how we evaluated (in terms real-time performance)

@@

We find that the DeepPicar is capable of 
completing control loops in under 33.$\overline{\mbox{33}}$ 
ms, or 30 hz, and can do so 100\% of the time.
Other tested embedded platforms, Intel Up and NVIDIA TX2, offer even
better performance, capable of supporting deep-learning based real-time
control up to 100 Hz control frequency on the TX2 when the GPU is used.
However, in all platforms, shared resource contention remains an
important issue as we observe up to 11.6X control loop execution time
increase, mostly due to increase in the nueral network inferencing
operation, when memory performance intensive applications are
co-scheduled on idle CPU cores.

>>>>

% DeepPicar introduction
In this paper, we present DeepPicar, a low-cost autonomous car
platform for research. From a hardware perspective,
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are affordable
components (less than \$100 in total).
The DeepPicar, however, employs state-of-the-art AI
technologies, including a vision-based end-to-end control system that
utilizes a deep convolutional neural network (CNN).
The network receives an image frame from a single forward
looking camera as input and generates a predicted steering angle
value as output at each control period in \emph{real-time}.
The network has 8 layers, about 27 million connections
and 250 thousand parameters (weights).
The network architecture is identical to that of NVIDIA's DAVE-2
self-driving car~\cite{Bojarski2016}, which uses a much more powerful
computer (Drive PX computer~\cite{drivepx}) than a Raspberry Pi~3.
We chose to use a Pi 3 not only because it is affordable, but also because it is representative
of today's mainstream low-end embedded multicore platforms found in
smartphones and other embedded devices.

@@

% how we trained (maybe moved to a later section)
We apply a standard imitation learning methodology to train the car to
follow tracks on the ground. We collect data for
training and validation by manually
controlling the RC car and recording the vision (from the webcam
mounted on the RC-car) and the human control inputs. We then train the
network offline using the collected data on a desktop computer, which
is equipped with a NVIDIA GTX 1060 GPU. Finally, the trained network is copied
back to the Raspberry Pi, which is then used to perform inference
operations---locally on the Pi---in the car's main control loop in
real-time. For real-time control, each inference operation must
be completed within the desired control period (e.g., 33.$\overline{\mbox{33}}$ ms
 period for 30 Hz control frequency).
% how we evaluated (in terms real-time performance)

@@

We find that the DeepPicar is capable of 
completing control loops in under 33.$\overline{\mbox{33}}$ 
ms, or 30 hz, and can do so 100\% of the time.
Other tested embedded platforms, Intel UP and NVIDIA TX2, offer even
better performance, and are capable of supporting deep-learning based 
real-time control up to 100 Hz control frequency on the TX2 when the GPU 
is used. However, in all platforms, shared resource contention remains 
an important issue as we observe up to 11.6X control loop execution time
increase, mostly due to increase in the neural network inferencing
operation, when memory performance intensive applications are
co-scheduled on idle CPU cores.
